---
title: "Flow diagram"
author: "Anshu Uppal"
date: "`r lubridate::today()`"
output: 
  html_document:
    code_folding: hide
knit: (function(input, ...) {
    rmarkdown::render(
      input, 
      output_dir = here::here("output")
    )
  })
---

```{r setup, results = "hide", message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE)  # Set default to not display code from chunks and not to display warnings
options(width = 300)
# Load packages and dataset ####
pacman::p_load(    # Installs / loads packages if they are not already installed / loaded
  rio,          # File import
  here,         # File locator
  skimr,        # get overview of data
  tidyverse,    # data management + ggplot2 graphics 
  gtsummary,    # summary statistics and tests
  rstatix,      # summary statistics and statistical tests
  janitor,      # adding totals and percents to tables
  scales,       # easily convert proportions to percents  
  flextable,    # converting tables to pretty images
  lubridate     # manipulate date objects
)

# Input flow diagram data from file previously generated using "Flow diagram.R"
dat <- tibble(readRDS(here("data", "Generated datasets", "flow_diagram.rds")))
# # Alternative is source it directly:
# source(here::here("code", "Flow_diagram.R"))
```

Remove suppressed (i.e. opted out)
```{r}
dat %>% count(send_status)
dat <- dat %>% filter(!send_status %in% c("Suppressed"))

```

Keep only those who did participate in the sero-cov-work or SP1,2,3,4 surveys --> This is our initial N for the flow diagram
```{r}
dat %>% count(serocov_work.x | serocov_pop.x | sp3_juin_2021.x | sp2_novdec_2020.x | sp4_avril_2022.x |pop_pilote.x
              | work_pilote.x
              )
dat <- dat %>% filter(serocov_work.x | serocov_pop.x | sp3_juin_2021.x | sp2_novdec_2020.x | sp4_avril_2022.x |pop_pilote.x
                      | work_pilote.x
                      )

paste0("N = ", length(dat$participant_id))
```


Exlude those outside our age range for inclusion and were not in salaried employment at baseline
```{r}
dat %>% summarize(under_18 = sum(age_inclusion < 18,na.rm = TRUE),
                  over_66 = sum(age_inclusion >= 67, na.rm = TRUE)
                  )
dat %>% summarize(not_salaried = sum(work_situation.x != "Salarié-e", na.rm = TRUE))

dat %>% mutate(over_66 = age_inclusion >= 67,
               not_salaried = work_situation.x != "Salarié-e",
               over65_st = age_invitation >=65
               ) %>% 
  count(
    # over_66
    over65_st
    # not_salaried
        )

dat <- dat %>% filter(age_invitation < 65 & work_situation.x == "Salarié-e")
paste0("N = ", length(dat$participant_id))

```

Remove those with invalid email --> but one person seems to have somehow done the questionnaire even after their email was declared invalid
```{r}
dat %>% count(send_status)
dat %>% group_by(Invited) %>% count(Responded)
dat <- dat %>% filter(!send_status %in% c("Bounced", "Failed"))
dat %>% group_by(Invited) %>% count(Responded)
paste0("N = ", length(dat$participant_id))

```

Remove those with no account (!!!!!need to double-check that this applies to all this filter group!!!!!!)
```{r}
dat %>% count(send_status)
dat <- dat %>% filter(!is.na(send_status))
paste0("N = ", length(dat$participant_id))

```

Overview of who was invited
```{r}
dat %>%
  ggplot(aes(x = date_soumission.x, fill = pop_source))+
  geom_histogram()+
  labs(title = "Inclusion questionnaire submission date", x = "Inclusion questionnaire submission date") +
  theme_bw()

dat %>%
  ggplot(aes(x = age_invitation))+
  geom_histogram()+
  labs(title = "Salarié-e: Age at invitation for Santé-travail questionnaire",
       x = "Age at invitation")+
  facet_wrap(.~pop_source)+
  theme_bw()
```

I asked Julien for some more information about why some of the salariée did not get the invite for the Santé-travail questionnaire (even though they submitted the Specchio inclusion questionnaire), and these are the main points of exclusion:  
  
* People without an email were not contacted
* People with an email but who did not create a Specchio account were not invited
* People who opted out of future questionnaires or opted out of the study were not contacted
* Age: 18 minimum, 66 maximum (!! taken from the time of the inclusion questionnaire)
* Some participants were recruited as part of the Schools and Kids studies, and these are a different context so they are not considered for Santé-Travail  

Filter for only those who responded
```{r}
dat %>% 
  count(Responded) %>% 
  mutate(percent = n / sum(n))
dat <- dat %>% filter(Responded == "Respondents")
paste0("N = ", length(dat$participant_id))

```
Exclude those who submitted inclusion Q within previous 12 months
```{r}
dat %>% 
  count(inc_st_diff_days > 1) %>% 
  mutate(percent = round(100 * n / sum(n),1))
dat <- dat %>% filter(inc_st_diff_days > 1)
```

Filter only for those employed within previous 12 months
```{r}
dat %>% 
  count(employed) %>% 
  mutate(percent = round(100 * n / sum(n),1))
dat <- dat %>% filter(employed == "Oui")
```

Filter only for those currently in a salaried position
```{r}
dat %>% 
  count(work_situation.y_dich) %>% 
  mutate(percent = round(100 * n / sum(n),1))
dat <- dat %>% filter(work_situation.y == "En activité salariée")
paste0("N = ", length(dat$participant_id))

```

Number of salariée employed before the pandemic
```{r}
dat %>% 
  count(wfh_change) %>% 
  mutate(percent = round(100 * n / sum(n),1))
dat <- dat %>% filter(!wfh_change %in% "Non concerné-e (vous n’aviez pas d’emploi avant la pandémie ou vous avez changé d’emploi)") 
paste0("N = ", length(dat$participant_id))

```



Filter out ages under 25 at the time of being invited to santé-travail questionnaire
Also filter out "Other" in sex (this is a weighting variable and levels can only be Male/Female)
```{r}
hist(dat$age_work, breaks = 20)
dat |> count(age_work >=25)
dat |> count(sex_en)
dat |> count(overcrowded)

dat <- dat %>% filter(age_work >= 25)
dat <- dat %>% filter(sex_en != "Other")
dat <- dat %>% filter(!is.na(overcrowded))

paste0("N = ", length(dat$participant_id))
```

Population-based recruitment source
```{r}
dat |> count(serocov_pop.x | pop_pilote.x | sp2_novdec_2020.x |sp3_juin_2021.x|sp4_avril_2022.x)
```

Mobilized worker-based recruitment source
```{r}
dat |> count(serocov_work.x | work_pilote.x)
```

Recruited in BOTH
```{r}
dat |> count((serocov_work.x | work_pilote.x) & 
               (serocov_pop.x | pop_pilote.x | sp2_novdec_2020.x |sp3_juin_2021.x|sp4_avril_2022.x))
```

Sensitivity N
```{r}
dat |> 
  group_by((serocov_pop.x | pop_pilote.x | sp2_novdec_2020.x |sp3_juin_2021.x|sp4_avril_2022.x)) |>
  count(percent_change_cat_r == "No change")
dat |> 
  group_by((serocov_pop.x | pop_pilote.x | sp2_novdec_2020.x |sp3_juin_2021.x|sp4_avril_2022.x)) |>
  count(pandemic_related_work_change == "No change")

dat |> 
  group_by((serocov_work.x | work_pilote.x)) |> 
  count(percent_change_cat_r == "No change")
dat |> 
  group_by((serocov_work.x | work_pilote.x)) |> 
  count(pandemic_related_work_change == "No change")
```

Apply the sensitivity filters and check N
```{r}
dat <- dat |> filter(
  pandemic_related_work_change == "No change",
  percent_change_cat_r == "No change"
)
dat |> count(serocov_pop.x | pop_pilote.x | sp2_novdec_2020.x |sp3_juin_2021.x|sp4_avril_2022.x)
dat |> count(serocov_work.x | work_pilote.x)
```